% ---------- Final gap-closer formalism ----------
\paragraph{QuotaGate framework.}
QuotaGate governs recommendation under a population-level uncertainty target by converting the target into a finite violation budget and allocating discretionary violations online.

\paragraph{Base controller.}
QuotaGateV6 prioritizes discretionary violations by the proxy-utility gap
\[
\Delta_u = U_u(S_u^{\mathrm{unc}}) - U_u(S_u^{\mathrm{comp}}).
\]

\paragraph{Outcome-calibrated extension.}
For an eligible request $u$, define exceedance and utility density as
\[
e_u = \max\{R(S_u^{\mathrm{unc}})-B,0\}, \qquad
d_u = \frac{\Delta_u}{e_u+\varepsilon}.
\]
Using validation requests only, fit an empirical bad-cost estimator
\[
\widehat{C}_{\mathrm{bad}}(e_u,d_u)
\]
that predicts the expected weighted bad exposure incurred by violating on request $u$.
OC-Quota then scores each opportunity by
\[
\mathrm{Score}_u = \Delta_u - \alpha \widehat{C}_{\mathrm{bad}}(e_u,d_u).
\]

\paragraph{Guarded-OC-Quota.}
Guarded-OC-Quota uses the same score but chooses $\alpha$ on validation under explicit guardrails:
(i) near-target compliance,
(ii) negligible held-out quality loss, and
(iii) bounded proxy-gap increase relative to QuotaGateV6.
Thus, the pacing skeleton and compliant-slate solver remain unchanged; only the prioritization rule for discretionary violations is modified.

\paragraph{Observed failure metrics.}
Binary bad exposure is
\[
\mathbf{1}\{R(S_u)>B\}\mathbf{1}\{\mathrm{Hit@}K_u=0\}.
\]
Severity-aware weighted bad exposure is
\[
\mathrm{WBE}_u = \max\{R(S_u)-B,0\}(1-\mathrm{Hit@}K_u).
\]
Risk-weighted miss is
\[
\mathrm{RWM}_u = R(S_u)(1-\mathrm{Hit@}K_u).
\]
These metrics quantify observed recommendation failures under uncertainty-budget violations.
